\vspace{-2cm}Digital Authoritarianism and United States Foreign Aid\vspace{-0.5cm}

### 2022-09-29 TheoryIdeas.tex
Updated

>>>>

9/28
If U.S. foreign aid policy is rational and related to internet freedom, then the U.S. must stand to gain from spending money on improving others' internet freedom. I argue that the U.S. benefits in two main ways from supporting internet freedom: protecting American technology's access to developing markets (possibly being encouraged by China to use Chinese technology instead) while ensuring that China faces resistance in continuing its economic growth (which is it's main goal of this project).

If this is true, then we should observe U.S. foreign aid spending patterns with one set of the following hypotheses:

\begin{align*}
    H_1a:\; & \text{U.S. aid should be associated with countries with high levels of internet freedom.}\\
    H_1b:\; & \text{U.S. aid should be associated with countries with low levels of internet freedom.}\\
    H_2a:\; & \text{U.S. aid should be associated with countries receiving high amounts of Chinese aid.}\\
    H_2b:\; & \text{U.S. aid should be associated with countries receiving low amounts of Chinese aid.}
\end{align*}

9/29
\section*{Theory}
Depending on how the literature review goes, we can mention our theory of why it is rational for the U.S. to engage in promoting internet freedom (aid effectually increases democracy, and democracy is good for business (American Big Tech)).
